%-------------------------------------------------------------------------------
%	SECTION TITLE
%-------------------------------------------------------------------------------
\cvsection{Experience \& Projects}


%-------------------------------------------------------------------------------
%	CONTENT
%-------------------------------------------------------------------------------
\begin{cventries}

%---------------------------------------------------------

  \cventry
    {Android Developer}
    {Toptal}
    {Remote}
    {November 2017 - PRESENT}
    {
      \begin{cvitems}
        \item {Be part of a world-class engineering network and work on hard technical challenges.}
        \item {Learnt new technologies such as OpenGL and FFmpeg to achieve optimal video processing and delight customers with results.}
        \item {Built and shipped production-ready grade software on a weekly basis.}
        \item {Used algorithms and data structures to improve performance of mobile app and optimize resources.}
        \item {Investigated, analyzed and quickly solved issues together as a team.}
        \item {Worked closely with BA/QA team members to create test plans and to ensure that the issues are properly identified, fixed, and tested.}
        \item {Built and grew large systems to satisfy the needs of customers.}
      \end{cvitems}
      \begin{cvsubentries}
        \cvsubentry{}{\href{https://play.google.com/store/apps/details?id=com.jumprope.android}
                     {\textbf{Jumprope}}{\dotsep}Allows to create and export professional-looking content quickly and easily.
                     {\dotsep}\icon{icons/android}\enskip\icon{icons/kotlin}}{October 2019 - PRESENT}{}
      \end{cvsubentries}
    }
  \cventry
    {Android Developer}
    {STRV}
    {Prague, Czech Republic}
    {July 2017 - November 2019}
    {
      \begin{cvitems}
        \item {Produced high-quality software that was unit tested, code reviewed, and checked regularly via continuous integration.}
        \item {Implemented and iterated with the whole team in an Agile environment to bring features from conception to launch.}
        \item {Led an Android team of four.}
        \item {Clearly communicated with the client to achieve a soft and outstanding development process.}
        \item {Contributed to an existing continuous integration framework by automating features as they are developed.}
        \item {Served as the technical leader for a Scrum team and actively participated in grooming sessions, sprint planning, daily scrums, and sprint reviews.}
        \item {Developed proof concepts for new and innovative ideas.}
        \item {Spoke publicly in meetups about Android and mobile development.}
      \end{cvitems}
      \begin{cvsubentries}
        \cvsubentry{}{\href{https://play.google.com/store/apps/details?id=com.legalzoom.kollaborate.prod}
                     {\textbf{LegalZoom}}{\dotsep}Allows post-purchase customers to track and manage their business formation
                     {\dotsep}\icon{icons/android}\enskip\icon{icons/kotlin}}{July 2017 - PRESENT}{}
      \end{cvsubentries}
    }
  \cventry
    {Android Developer}
    {Condor Labs}
    {Medellín, Colombia}
    {March 2016 - September 2017}
    {
      \begin{cvitems}
        \item {Designed, implemented and maintained a SQLite database for storing data on mobile disk.}
        \item {Designed, developed, and supported Android applications to track the continuing education of health professionals.}
        \item {Improved the functionality of Android applications using model-view-presenter pattern and clean architecture.}
        \item {Built components using ReactiveX (RxJava 2) and a dependency injection with Dagger 2.}
        \item {Implemented Firebase push notifications for Android applications.}
        \item {Created functional testing automated tasks with Gherkin notation using Gradle, Calabash, and Cucumber.}
      \end{cvitems}
      \begin{cvsubentries}
        \cvsubentry{}{\href{https://play.google.com/store/apps/details?id=com.cebroker.app}
                     {\textbf{CE Broker}}{\dotsep}Allows health professionals to track continuing
                     education{\dotsep}\icon{icons/android}}{March 2016 - September 2017}{}
        \cvsubentry{}{\href{https://play.google.com/store/apps/details?id=com.evercheck}
                      {\textbf{EverCheck}}{\dotsep}Allows employers to manage license compliance
                      and monitor healthcare licenses{\dotsep}\icon{icons/android}}
                      {August 2016 - September 2017}{}
        \cvsubentry{}{\textbf{EverCheck Wallet}{\dotsep}Allows health professionals to update
                      Heart Card certifications{\dotsep}\icon{icons/android}}
                      {April 2016 - September 2017}{}
      \end{cvsubentries}
    }
  \cventry
    {Full-stack Developer}
    {Talos Digital, Inc.}
    {Medellín, Colombia}
    {July 2015 - March 2016}
    {
      \begin{cvitems}
        \item {Developed AngularJS applications consuming RESTful web services.}
        \item {Automated tasks for continuous integration and deployment with Jenkins.}
        \item {Built and deployed applications using Docker containers.}
        \item {Implemented RESTful APIs, services, and gems using Ruby on Rails.}
        \item {Participated in a six-month internship program that was done in the company.}
      \end{cvitems}
    }
  \cventry
    {Teacher Assistant in Data Structures and Algorithms II}
    {EAFIT University}
    {Medellín, Colombia}
    {January 2015 - June 2015}
    {
      \begin{cvitems}
        \item {Taught students about data structures such as maps, sets, trees, queues, stacks, and lists.}
        \item {Explained common computer science algorithms for graphs, dynamic programming, pattern matching, and ad hoc solutions.}
      \end{cvitems}
    }
  \cventry
    {Android Junior Developer}
    {IdeasLab}
    {Medellín, Colombia}
    {July 2013 - June 2014}
    {
      \begin{cvitems}
        \item {Learned Android SDK basics and implemented simple Android applications.}
        \item {Gained a basic knowledge set about graphic Android components and RESTful API usage from an Android app.}
      \end{cvitems}
    }
\end{cventries}
